Setup Honeypot: Team Contagiarium

### 2011-11-01 Setup_honeypot.tex
added kernel module part

>>>>

\subsection{Kernel Module}

For HI phase, we would like to have a way to audit the commandline. 
To make it harder to detect this we would like to do this in the kernel.
We could edit auditd for the user, but this wil be too noticiable. 
A tool we can use is Sebek, but this is outdated and not maintained.
So we have started work on our own kernel module, which will hopefully be ready before we start the HI phase.
